---
server: shiny
filters: [surveydown]
---

```{r}
#| context: setup
#| echo: false
#| warning: false
#| message: false

# Run this in your R Console to install the latest version of the package:
# remotes::install_github("surveydown-dev/surveydown", force = TRUE)

# Run this to install or update the Quarto extension to the latest version:
# surveydown::sd_update_extension()

# Load the package
library(surveydown)

# Run initial setup function (essential - do not delete)
sd_setup()
```

::: {#welcome .sd-page}

# Welcome to our survey!

This is a simple demonstration of a surveydown survey. It has two pages with one question on each page.

Here is a basic "multiple choice" question, created using `type = 'mc'` inside the `sd_question()` function:

```{r}
sd_question(
  type  = 'mc',
  id    = 'penguins',
  label = "Which type of penguin do you like the best?",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo'
  )
)
```

<br>

You need to insert next buttons with `sd_next()` and set the `next_page` argument to the name of the page you want to go to next.

```{r}
sd_next(next_page = 'page2')
```

:::

::: {#page2 .sd-page}

This is another page in your survey.

{surveydown} supports many types of questions. For example, here is a simple `text` type question:

```{r}
sd_question(
  type  = "text",
  id    = "silly_word",
  label = "Write a silly word here:"
)
```
 
<br>

```{r}
sd_next(next_page = 'end')
```

:::

::: {#end .sd-page}

This it the last page in the survey

:::

```{r}
#| context: server

##################
# database setup #
##################

# surveydown stores data on a database that you define at https://supabase.com/
# To connect to a database to store the survey data, update this with details
# from your supabase account and database. See documentation for details at
# https://surveydown.org/database

# db <- sd_database(
#   host       = "",
#   dbname     = "",
#   port       = "",
#   user       = "",
#   table_name = "",
#   gssencmode = "prefer" # Change to "disable" if there's connection problem.
# )

# If you don't have a database setup you can just leave the function blank.
# When testing without a database connected, a data.csv file will be
# written to the project directory so you can preview the response data.

db <- sd_database()

################
# config setup #
################

# Use the sd_config() function to customize features in your survey, like
# logic to conditionally display questions or skip to pages based on responses
# to skip other questions in your survey. See documentation for details at
# https://surveydown.org/config

config <- sd_config()

####################################
# Don't change anything below here #
####################################

# The sd_server function initiates your survey - don't change this

sd_server(
  input   = input,
  output  = output,
  session = session,
  config  = config,
  db      = db
)
```
